---
title: "Exploratory Data Analysis"
author: "Mathew Yang"
output: html_document
---

```{r}
library(ggplot2)
library(reshape2)
library(readr)
library(GGally)
#set working directory
#setwd("C:\\Users\\matt\\Documents\\BIOE530\\project\\data")
```

I will be using the Wisconsin Breast Cancer dataset for exploratory data analysis. The goal of this is to gain a deeper understanding of the data I will be working with. 

```{r}
setwd("C:\\Users\\me\\Documents\\Wisconsin-Breast-Cancer\\Wisconsin-Breast-Cancer\\data")
wdbc = read.csv("wdbc.data", header= FALSE)
```
There are 569 patients in this dataset with 32 features. Features 1 and 2 are the ID number and breast cancer diagnosis for the patient. The remaining 30 features are computed values from images of cell nuclei. The mean, standard error, and max values were computed for each of the 10 real-valued features, resulting in a total of 30.

Real-value features.
	[3,13,23] radius (mean of distances from center to points on the perimeter)
	[4,14,24] texture (standard deviation of gray-scale values)
	[5,15,25] perimeter
	[6,16,26] area
	[7,17,27] smoothness (local variation in radius lengths)
	[8,18,28] compactness (perimeter^2 / area - 1.0)
	[9,19,29] concavity (severity of concave portions of the contour)
	[10,20,30] concave points (number of concave portions of the contour)
	[11,21,31] symmetry 
	[12,22,32] fractal dimension ("coastline approximation" - 1)
	
```{r}
#Divide malignant vs benign
malignant.all = vector(length=0)
benign.all = vector(length=0)
for (i in 1:nrow(wdbc)){
  if (wdbc[i,2] == 'M'){
    malignant.all = rbind(malignant.all, wdbc[i,])
  } 
  else {
    benign.all = rbind(benign.all, wdbc[i,])
  }
}
```

```{r}
ggplot(wdbc, aes(V2)) + geom_bar(aes(fill=V2)) +
            labs(title = 'Diagnosis', y='Number of People', x='Type (B=Benign, M=Malignant)')
```

```{r}
#Only interested in first 11 columns (mean)
benign = benign.all[,3:12]
malignant = malignant.all[,3:12]

#only the means
wdbc.means = wdbc[3:12]
wdbc.means.melt = melt(wdbc.means)
```

```{r}
ggplot(melt(benign[,2:4]), aes(x=value, fill=variable )) +   geom_histogram() +
      facet_grid(variable~.) +
      labs(title='Histogram of Benign', x='Frequency', y='Expression Value')
ggplot(melt(malignant[,2:4]), aes(x=value, fill=variable )) +   geom_histogram() +
      facet_grid(variable~.) +
      labs(title='Histogram of Malignant', x='Frequency', y='Expression Value')
```


```{r}
ggplot(melt(benign[,2:3])) + geom_boxplot(aes(x=variable, y=value))+
      labs(title='Histogram of Benign', x='Variable', y='Value')
ggplot(melt(benign[4])) + geom_boxplot(aes(x=variable, y=value))+
      labs(title='Histogram of Benign', x='Variable', y='Value')
```
```{r}
ggplot(melt(malignant[,2:3])) + geom_boxplot(aes(x=variable, y=value))+
      labs(title='Histogram of Malignant', x='Variable', y='Value')
ggplot(melt(malignant[4])) + geom_boxplot(aes(x=variable, y=value))+
      labs(title='Histogram of Malignant', x='Variable', y='Value')
```


```{r}
#Normalize data before PCA


```


Principal components analysis
```{r}
#Start PCA
#pca.benign = prcomp(benign)
#pca.malignant = prcomp(malignant)
#summary(pca.benign)
#summary(pca.malignant)
```
`

