---
title: "Logistic regression"
author: "Mathew Yang"
date: "November 27, 2017"
output: html_document
---

```{r}
library(caret)
library(pROC)
#Load data
wdbc = read.csv("data/wdbc.data", header= FALSE)
#only the means
wdbc.means = wdbc[2:12]
```

```{r}
#PCA
pca.model = prcomp(wdbc.means[,2:11])
summary(pca.model)
biplot(pca.model, scale = 0)                
```
PCA reveals that there are 3 principal components that make up almost the entirety of the variance (V6, V5, V4). We will use these 3 PCs in our model.

#Logistic Regression
```{r}
#Logistic regression on means.
#Train and test on same dataset.
cancer.fit = glm(V2 ~ pca.model$x[,1] + pca.model$x[,2] + pca.model$x[,3], data=wdbc.means, family= binomial)
summary(cancer.fit)
```

V4,V6,V7,V10 showed significance. This was training and testing on the same dataset. 
```{r}
#Gives probabilities that the observation is a malignant tumor. Probability close to 1 is malignant, 0 is benign.
cancer.probs = predict(cancer.fit, type = "response")

#Create a vector of 569 Benign elements
cancer.pred=rep("B",569)

#Transform all the ones greate than 0.5 to Malignant.
cancer.pred[cancer.probs>0.5]="M"
```
Confusion Matrix
```{r}
table(cancer.pred, wdbc$V2)
```

Training error rate is 1 - (334+181)/569 = ??, which means that the model was capable of correctly guessing M or B almost X?% of the time. This needs to be retested via crossvalidation or LOOCV.
```{r}
# Different PCA method
preProc <- preProcess(wdbc.means[2:11], method="pca", pcaComp = 3)
trainPC <- predict(preProc, wdbc.means[2:11])
testPC <- predict(preProc, wdbc.means[2:11])
# add the diagnosis into the trainPC data
trainPC <- data.frame(trainPC, wdbc.means$V2)
```

```{r}
#10-fold cross validation
ctrl <- trainControl(method = "repeatedcv", number = 10, savePredictions = TRUE)

#Perform logistic regression on cross-validated data
mod_fit <- train(wdbc.means.V2~ ., 
                 data=trainPC, preProc="pca", method="glm", family="binomial",
                 trControl = ctrl)
summary(mod_fit)
```

```{r}
pred = predict(mod_fit, type = "prob")
actual = as.numeric(wdbc.means$V2)-1
roc.log <- roc(actual, pred$B)
```

```{r}
# Plot ROC
plot.roc(roc.log, xlab = "False Positive Rate", ylab="True Positive Rate", main="ROC Curve", print.auc=TRUE)
#Get AUC
auc(roc.log)
```

```{r}

```

